```{r}
library(tidyverse)
library(dplyr)
```

#1  Read in `districts.csv` into a tibble named `districts`.

```{r}
districts = read.csv("../data/districts.csv")
districts
```
#2 Notice that the first row corresponds to the whole State of Tennessee. Remove this row and save the result back to `districts`.
  
```{r}
districts <- districts |> 
  filter(system != 0)

districts
```

#3 How many districts have a proficiency rate of at least 80% for both alg_1 and eng_1?

```{r}
districts |> 
  filter(alg_1 >= 80, eng_1 >= 80)
```
13 counties had a proficiency rate of atleast 80 in both algebra 1 and english 1

#4 How many districts have a proviciency rate less than 50% for either alg_1 or eng_1?

```{r}
districts |> 
  filter(alg_1 <= 50 | eng_1 <= 50)
```
 8 counties had less than 50% proficiency in either alg 1 or eng 1
 
 
 
 #5 Which district has the lowest graduation rate?
 
```{r}

districts |> 
  arrange(grad)
```
 If we assume that "Tenn School for Blind" is not a district, than the district with lowest graduation rate is Achievement School District.
 
 
 #6 Within the Mid Cumberland region, which district has the highest ACT composite?

```{r}
 mid_cumb <- districts |> 
  filter(region == 'Mid Cumberland') |> 
  arrange(desc(act_composite))

mid_cumb
```
 Williamson county had the highest ACT composite score out of the mid cumberland region.
 
 
 #7 Create a scatter plot to compare alg_1 proficiency rates to alg_2 rates. What do you notice? Facet this plot by region. Does anything stand out when you facet the plots?
 
```{r}


ggplot(districts, aes(x = alg_1, y = alg_2)) + geom_point()
```
  It seems that when one profeciency percentage goes up the other one will as well.
  
```{r}
ggplot(districts, aes(x = alg_1, y = alg_2)) + geom_point() + facet_wrap(~region)
```
  Despite some having more or less points, they all have a similar upwards y=x shape OTHER THAN upper cumberland, where some of its highest alg_1 percentages are the lowest alg_2 percentages.
  
#8 When creating this bar chart you may have noticed that some districts have missing enrollment values. For how many districts is this the case?

```{r}
districts |> 
  filter(is.na(enrollment))
```
There are 4 districts with no enrollment values. 

#9 A lot of rows are missing additional values. Which district has the largest number of missing values (across all variables)? Hint: you might want to look at rowwise and c_across to answer this question.

Used this website for help: https://rstats101.com/count-number-of-missing-values-per-row-in-a-dataframe/

```{r}
districts |> 
  rowwise() |> 
  mutate(n_NAs = sum(is.na(across(everything())))) |> 
  arrange(desc(n_NAs))
  
```
The district that has the largest number of empty values is the "West Tenn School for Deaf" but if we don't count that as a district, than there are a lot tied for 10.

#10 What is the mean graduation rate across all districts? What might be wrong with using just the regular mean to assess average graduation rates?

```{r}
districts |> 
  summarize(avg_grad = mean(grad, na.rm = TRUE))
```
It might be skewed because some districts might be much smaller and have different conditions, which could make it higher than normal. 

#11

```{r}
weighted.mean(x=districts$grad, w=districts$enrollment)
```

 